Syntax-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-09 paper/paper.tex
structured second half of the paper

% TODO: reformulate and add possiby graphical example

\subsection{Generating grammar rules}

\section{Evaluation} \label{evaluation}
% we use udpipe

\section{Conclusions} \label{conclusions}
% tangible output and were it is

>>>>

% TODO: reformulate and add possibly graphical example

\subsection{Generating grammar rules}
The CE module described so far outputs pairs of UD trees. 
While converting them to GF Abstract Syntax Trees (ASTs) is the \texttt{gf-ud}'s core functionality, to build a compilable GF translation lexicon it is necessary to turn such trees into grammar rules.

In order to do that, our grammar generation module requires a morphological dictionary of the languages at hand and an \textit{extraction grammar}. 
What we refer to as an extraction grammar is of course a GF grammar, whose
objective is to define the set of basic categories and syntactic rules the entries of the automatically generated lexicon is going to use.

\section{Evaluation} \label{evaluation}
\subsection{Data}
% PUD treebanks
% plans (+UDPipe)
% langs

\subsection{Evaluating CE} % TODO: find better title?
\subsubsection{Experimental setup} % TODO: find better title?
% metrics & methods
\subsubsection{Results}
% PUD (incl. reason-wise?): independent, comparison with SMT
% RAW
\subsubsection{Discussion}

\subsection{MT experiments}
\subsubsection{Experimental setup}
\subsubsection{Results}
\subsubsection{Discussion}

\section{Conclusions} \label{conclusions}
% tangible output and were it is on github
% summary of process and discussions
\subsection{Future work}
